---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
First load the tidyverse in the command line. Then, check your working directory to make sure it is correct, also in the command line.

```{r load tidyverse, include=FALSE}
library(tidyverse)
getwd()
```

## Problem 1: Creating the dataframe

First, create the random_samp variable that contains a random sample of 10 numbers from a normal distribution whose standard deviation is 0.7.

Then, define variable nonzero equal to all random_samp variables greater than zero. 

FINISH EXPLAINING OUT YOUR CODE

```{r create dataframe}

example_df = tibble(
  vec_random = rnorm(10, sd = .7),
  lgl_nonzero = vec_random > 0,
  vec_char = c("Catherine" , "Kate", "Katie", "Cat", "Katherine", "Kathryn", "Catharine", "Cathy", "Kitty", "Catie"),
  vec_factor = factor(c("best", "best", "best", "good", "good", "good", "best", "better", "best", "best")),
  )
print(example_df)
```

```{r taking the mean}
mean(pull(example_df, vec_random))
mean(pull(example_df, lgl_nonzero))
mean(pull(example_df, vec_char))
mean(pull(example_df, vec_factor))
```

