---
title: "Catherine Lucey, P8105 Homework 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
First load the tidyverse in the command line. Then, check your working directory to make sure it is correct, doing so in the command line as well.

## Problem 1: Creating the dataframe

First, create the random_samp vector that contains a random sample of 10 numbers from a normal distribution whose standard deviation is 0.7.

Then, define vector "nonzero" to indicate whether each random_samp variable is greater than zero. 

Next, define a character vector "vec_char" listing the possible spellings and nicknames for the name Catherine.

Lastly, assign a factor vector with three levels, "ok", "better", and "best" to describe each Catherine variation. 


```{r create dataframe}

example_df = tibble(
  vec_random = rnorm(10, sd = .7),
  lgl_nonzero = vec_random > 0,
  vec_char = c("Catherine" , "Kate", "Katie", "Cat", "Katherine", "Kathryn", "Catharine", "Cathy", "Kitty", "Catie"),
  vec_factor = factor(c("best", "better", "better", "better", "ok", "ok", "ok", "ok", "better", "best")),
  )
print(example_df)

```

```{r taking the mean}
mean(pull(example_df, vec_random))
mean(pull(example_df, lgl_nonzero))
mean(pull(example_df, vec_char))
mean(pull(example_df, vec_factor))
```
```{r numerics}
set.seed(6)
as.numeric(example_df, vec_random)
as.numeric(example_df, lgl_nonzero)
as.numeric(vec_factor)
print(as.numeric(vec_char))
```

# Problem 2: Plotting Data
You can make dataframes contained within the package viewable using View("df_name"); this will open the data frame in a new window. The variables and dataframes contained within the package can be viewed in the "environment" panel. 

```{r}
data("penguins", package = "palmerpenguins")
skimr::skim(penguins)
```


skimr::pull(penguins, penguins_data)

View just gives you a sample, glimpse() gives you all of the variables
summary() is also helpful

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
